---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-",
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

# memery

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/memery.svg?branch=master)](https://travis-ci.org/leonawicz/memery)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/memery?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/memery)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/memery/master.svg)](https://codecov.io/github/leonawicz/memery?branch=master)

The `memery` package is used for generating internet memes suited specifically to data analysts.

`merery` offers the following:

* Memes can use jpg or png inputs for the background image.
* You can control the font family.
* The classic meme font family, Impact, with shadow/outline effect for the meme text label is available and is the default.
* Shadow effect is available for other fonts as well.
* Arbitrary number of text labels and placement using vectorized arguments; ideal for top/bottom or title/subtitle meme text pairs.
* Memes may optionally include a superimposed inset plot (ggplot object).
    * The default is to draw the optional plot directly on top of the background image, so it is recommended to use a transparent or semi-transparent background color for the ggplot panel and plot regions.
    * Alternatively, if you want a solid background for the plot inset, size and placement can be adjusted to your needs.
* Output file can be jpg or png.

*Note: `memery` is in early development.*

## Installation

You can install memery from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/memery")
```
